|

### 2021-02-09 appendix/appendix.Rmd
add het fx exp02 and exp03, small edits

This appendix contains the `R` code required to replicate the results we
present in "_Casting the First Stone: Understanding Attitudes towards Lynching
in Brazil_". This file also includes the descriptive statistics of our sample,
the average marginal component effects (AMCEs) for our conjoint experiment,
additional subgroup analyses for all three experiments, and a standard report
which follows APSA's guidelines for experimental research [@gerber2014reporting].

@@

We estimate a latent Dirichlet allocation (LDA) model to identify the
three most important topics in our corpus. The first topic includes words that
describes lynching perpetrators, as it contains the words like _polícia_
(police), _pessoas_ (people), and _família_ (family). The second topic
identifies the same words we associate with respondents who are against
lynchings, such as _nenhum_ (none), _opção_ (choice), _não_ (no), and _contra_
(against). The last topic, in contrast, refer to victim and crime
characteristics, which have also appeared in our previous estimations. Some of
the most common words in this group are _crime_ (crime), _criança_ (child),
_estupro_ (rape), _vítima_ (victim), _porque_ (because), _idoso_ (elderly),
_grave_ (serious), and _molestar_ (molest).

As our results show, respondents decide which individual deserves punishment
based on factors related to the crime he/she committed, specially the crime
victim. There is also a group of respondents that oppose lynchings in
principle, who affirm that lynchings are not justified.

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Latent Dirichlet allocation
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
```
\normalsize

@@

@@

\footnotesize
```{r exp02-bart02, warning=F, error=F, message=F, cache=T}
df_exp02_slow_justice <- df_exp02_het %>%
  mutate(exp02_slow_justice_treat = as.numeric(exp02_slow_justice_treat)) %>%
  drop_na(exp02_slow_justice_treat)

@@

# Race
# summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
              # group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
              # n.chains = 5L, seed = 144))

@@

@@

# Household Income
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income2,
              group.by = household_income2, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

@@

@@

Our results are available in table XXX below.

# Session Information
\label{sec:session-info}

>>>>

This appendix contains the `R` code required to replicate the results we
present in "_Casting the First Stone: Understanding Attitudes towards Lynching
in Brazil_". This file also includes the descriptive statistics of our sample,
the average marginal component effects (AMCEs) for our conjoint experiment,
and additional subgroup analyses for all three experiments.

@@

We estimate a latent Dirichlet allocation (LDA) model to identify the three
most important topics in our corpus. The first topic includes words that refer
to victim and crime characteristics, many of which have also appeared in our
previous estimations. Some of the most common words in this group are _crime_
(crime), _criança_ (child), _estupro_ (rape), _vítima_ (victim), _porque_
(because), _idoso_ (elderly), _grave_ (serious), and _molestar_ (molest). When
we count the number of topics in the corpus, we see that this is the
predominant one. The second topic identified by the model describes lynching
perpetrators, as it contains the words like _polícia_ (police), _pessoas_
(people), and _família_ (family). The third topic identifies the same words we
associate with respondents who are against lynchings, such as _nenhum_ (none),
_opção_ (choice), _não_ (no), and _contra_ (against). As our results show,
respondents decide which individual deserves punishment based on factors
related to the crime he/she committed, specially the crime victim. There is
also a group of respondents that oppose lynchings in principle, who affirm that
lynchings are never justified.

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Latent Dirichlet allocation
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
table(topics(tmod_lda))
```
\normalsize

@@

# Previous Victimization
df_exp02_police2 <- df_exp02_police %>% drop_na(previous_victim_dummy)
summary(bartc(exp02_outcomes, exp02_police_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_police2,
              n.chains = 5L, seed = 144))

@@

\footnotesize
```{r exp02-bart02, warning=F, error=F, message=F, cache=T}
# Remove "Indigenous" and "Other" from `race` as they only
# have 1 observation each. The model cannot be estimated otherwise.
df_exp02_slow_justice <- df_exp02_het %>%
  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
  mutate(exp02_slow_justice_treat = as.numeric(exp02_slow_justice_treat)) %>%
  drop_na(exp02_slow_justice_treat)

@@

# Race
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

@@

# Previous Victimization
df_exp02_slow_justice2 <- df_exp02_slow_justice %>% drop_na(previous_victim_dummy)
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_slow_justice2,
              n.chains = 5L, seed = 144))

@@

# Household Income
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

@@

# Previous Victimization
df_exp02_small_punishment2 <- df_exp02_small_punishment %>% drop_na(previous_victim_dummy)
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_small_punishment2,
              n.chains = 5L, seed = 144))

@@

Our results are available in table \ref{tab:exp03main}. Reminding respondents
of the legal consequences of lynchings has a strong, negative effect on
individual levels of lynching support. We see a reduction of about 4.5%, which
corresponds to an 11% change when compared to the baseline levels. Our second
treatment condition, reminding subjects of human rights guarantees, has no
statistically significant effect. Informing respondents that lynchings can
trigger a cycle of violence also has a large negative effect. It decreases
lynching support by 3%, which is an 8% reduction in comparison with the control
group. When we combine all treatments, we still detect a negative impact of the
treatment conditions.

\footnotesize
```{r exp03-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp03 <- df1 %>%
  mutate(exp03_outcomes = coalesce(exp03_control, exp03_constitution,
                                   exp03_rights, exp03_vendetta),
         exp03_any_treat = case_when(!is.na(exp03_control) ~ "0",
                                     !is.na(exp03_constitution) ~ "1",
                                     !is.na(exp03_rights) ~ "1",
                                     !is.na(exp03_vendetta) ~ "1",
                                     TRUE ~ NA_character_),
         exp03_constitution_treat = case_when(!is.na(exp03_control) ~ "0",
                                              !is.na(exp03_constitution) ~ "1"),
         exp03_rights_treat = case_when(!is.na(exp03_control) ~ "0",
                                        !is.na(exp03_rights) ~ "1"),
         exp03_vendetta_treat = case_when(!is.na(exp03_control) ~ "0",
                                          !is.na(exp03_vendetta) ~ "1"))

m1 <- lm(exp03_outcomes ~ exp03_constitution_treat, data = df_exp03)
m2 <- lm(exp03_outcomes ~ exp03_rights_treat, data = df_exp03)
m3 <- lm(exp03_outcomes ~ exp03_vendetta_treat, data = df_exp03)
m4 <- lm(exp03_outcomes ~ exp03_any_treat, data = df_exp03)

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp03main",
          title = "Experiment 03 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Constitution and penal code", "Human rights",
                               "Vendettas", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

In this section, we explore whether our pre-treatment covariates impact the
treatment effect. We use the same flexible approach we employed in the previous
experiment, and estimate all models using Bayesian Additive Regression Trees
(BART). The algorithm produces average treatment effects for each category in
the moderator variables.

### Treatment 01: Legal Punishment for Lynching Perpetrators

We find no evidence of heterogeneous effects in this treatment condition. All
coefficients are largely similar across all model specifications.

\footnotesize
```{r exp03-bart01, warning=F, error=F, message=F, cache=T}
df_exp03_het <- df_exp03 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"))

df_exp03_constitution <- df_exp03_het %>%
  mutate(exp03_constitution_treat = as.numeric(exp03_constitution_treat)) %>%
  drop_na(exp03_constitution_treat)

# Gender
summary(bartc(exp03_outcomes, exp03_constitution_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp03_outcomes, exp03_constitution_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp03_outcomes, exp03_constitution_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp03_outcomes, exp03_constitution_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp03_outcomes, exp03_constitution_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp03_outcomes, exp03_constitution_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp03_constitution2 <- df_exp03_constitution %>% drop_na(previous_victim_dummy)
summary(bartc(exp03_outcomes, exp03_constitution_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_constitution2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp03_outcomes, exp03_constitution_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp03_outcomes, exp03_constitution_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp03_constitution,
              n.chains = 5L, seed = 144))
```
\normalsize

### Treatment 02: Human Rights

Our results show no presence of heterogeneous effects.

\footnotesize
```{r exp03-bart02, warning=F, error=F, message=F, cache=T}
df_exp03_rights <- df_exp03_het %>%
  mutate(exp03_rights_treat = as.numeric(exp03_rights_treat)) %>%
  drop_na(exp03_rights_treat)

# Gender
summary(bartc(exp03_outcomes, exp03_rights_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp03_outcomes, exp03_rights_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp03_outcomes, exp03_rights_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp03_outcomes, exp03_rights_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp03_outcomes, exp03_rights_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp03_outcomes, exp03_rights_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp03_rights2 <- df_exp03_rights %>% drop_na(previous_victim_dummy)
summary(bartc(exp03_outcomes, exp03_rights_treat, previous_victim_dummy, 
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_rights2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp03_outcomes, exp03_rights_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp03_outcomes, exp03_rights_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp03_rights,
              n.chains = 5L, seed = 144))
```
\normalsize

### Treatment 03: Vendettas

We do not find considerable heterogeneity in the these results. Overall, the
three treatment conditions are very stable, thus we are confident that the
main results are not driven by any particular group.

\footnotesize
```{r exp03-bart03, warning=F, error=F, message=F, cache=T}
df_exp03_vendetta <- df_exp03_het %>%
  mutate(exp03_vendetta_treat = as.numeric(exp03_vendetta_treat)) %>%
  drop_na(exp03_vendetta_treat)

# Gender
summary(bartc(exp03_outcomes, exp03_vendetta_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp03_outcomes, exp03_vendetta_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp03_outcomes, exp03_vendetta_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp03_outcomes, exp03_vendetta_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp03_outcomes, exp03_vendetta_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp03_outcomes, exp03_vendetta_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp03_vendetta2 <- df_exp03_vendetta %>% drop_na(previous_victim_dummy)
summary(bartc(exp03_outcomes, exp03_vendetta_treat, previous_victim_dummy, 
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_vendetta2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp03_outcomes, exp03_vendetta_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp03_outcomes, exp03_vendetta_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp03_vendetta,
              n.chains = 5L, seed = 144))
```
\normalsize

# Session Information
